Dynamics Analysis: The Sound of Teaching Music 2

### 2022-07-27 experiment-1/analysis/stats/dynamics.Rmd
correct typos
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
remove unnessesary tags
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update dynamics analysis to remove warnings
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistic
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("emmeans")) {install.packages("emmeans"); require("emmeans")}

# chunk option
knitr::opts_chunk$set(warning = FALSE)
```

@@

```{r, echo = FALSE, warning = FALSE}
# normalise diff by KV range
vel_diff_dyn_trial$NormalisedDiff <- 0
for (i in unique(vel_diff_dyn_trial$SubNr)){
  for (m in unique(vel_diff_dyn_trial[SubNr == i]$TrialNr)){
    # teaching
    # FtoP
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean))
    # PtoF
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean))

    # performing
    # FtoP
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean))
    # PtoF
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean))

    # error messages for non-existing trials but it's not reflected on vel_diff_dyn_trial anyway
  }
}

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistic
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("emmeans")) {install.packages("emmeans"); require("emmeans")}
```

@@

```{r, echo = FALSE}
# normalise diff by KV range
vel_diff_dyn_trial$NormalisedDiff <- 0
for (i in unique(vel_diff_dyn_trial$SubNr)){
  for (m in unique(vel_diff_dyn_trial[SubNr == i]$BlockNr)){
    for (n in unique(vel_diff_dyn_trial[SubNr == i & BlockNr == m]$TrialNr)){
      # FtoP
      vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean)-min(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean))
      # PtoF
      vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean)-min(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean))
    }
  }
}

### 2022-07-27 experiment-2/analysis/stats/dynamics.Rmd
update dynamics analysis to remove warnings
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### [Sequence plot](#sequence)

- [Additional analysis based on reviewers' comments](#additional)

@@

## Normalised KV difference per trial

```{r, echo = FALSE, warning = FALSE}
# normalise diff by KV range
vel_diff_dyn_trial$NormalisedDiff <- 0
for (i in unique(vel_diff_dyn_trial$SubNr)){
  for (m in unique(vel_diff_dyn_trial[SubNr == i]$TrialNr)){
    # teaching
    # FtoP
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean))
    # PtoF
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching" & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "teaching"]$Mean))

    # performing
    # FtoP
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean))
    # PtoF
    vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing" & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean)-min(vel_dyn_trial[SubNr == i & TrialNr == m & Condition == "performing"]$Mean))

    # error messages for non-existing trials but it's not reflected on vel_diff_dyn_trial anyway
  }
}

>>>>

## [Sequence plot](#sequence)

## [Additional analysis](#additional)

@@

## Normalised KV difference per trial
```{r, echo = FALSE}
# normalise diff by KV range
vel_diff_dyn_trial$NormalisedDiff <- 0
for (i in unique(vel_diff_dyn_trial$SubNr)){
  for (m in unique(vel_diff_dyn_trial[SubNr == i]$BlockNr)){
    for (n in unique(vel_diff_dyn_trial[SubNr == i & BlockNr == m]$TrialNr)){
      # FtoP
      vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "FtoP"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "FtoP"]$Mean/(max(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean)-min(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean))
      # PtoF
      vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "PtoF"]$NormalisedDiff <- vel_diff_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n & Subcomponent == "PtoF"]$Mean/(max(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean)-min(vel_dyn_trial[SubNr == i & BlockNr == m & TrialNr == n]$Mean))
    }
  }
}
